### 2012-12-27 MSWL_ECO_lesson4.tex
updated #6 - Summary: Cost/benefit analysis
Comment code in spanish to avoid compiling error using verbatim package.
Add my name to the authors and translate from spanish to english.

@@

En Software no compras el producto, valoras el servicio que te ofrece.

La organizaciónd el modelo de Software Libre permite ofrecer mejores servicios:
\begin{itemize}
    \item Usuarios que se convierten en clientes.
    \item escalabilidad en identificación de fallos. Los programas de éxito suelen tener menos errores, el éxito medido en usuario.
    \item Compartir riesgos y costes de producción. Entre los actores se comparte el gasto del desarrollo.
    \item Prácticas monopolísticas muy difíciles. Un fork permite escapar de la monopolización del producto.
\end{itemize}

\emph{Si no tienes usuarios no tienes modelo de negocio.}

>>>>

% I've commented this section to avoid compiling problems. commet is defined in
% verbarim package, use it as a normal item after importing in main file.

\begin{comment}

@@

In Software you don't purchase the product , you evaluate the service that product offers.

The organization of Free Software model allows offering best services:
\begin{itemize}
    \item Users who become clients.
    \item Scalability in failure identification. Successful programs use to have less errors, where success measured in user.
    \item Share risks and production costs. Development cost is shared among the actors.
    \item Monopolistic practices are very difficult. A fork allows to escape from product monopolization.
\end{itemize}

\emph{If you don't have users , you don't have any available business model.}
\end{comment}
